On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-03-27 engineering.tex
definition of channels

While \emph{agents} and \emph{communication} between agents are described and
defined in Section~\ref{sec:theory}, both the concepts of \emph{port} (depicted in Figure~\ref{fig:ioports},
\emph{channel}, \emph{functional and physical architecture}, and
\emph{functional block} have not yet been defined with respect to the
$\abf$-theory.  Informally, a channel identifies the place where the
communication takes place.  In this work we only consider mono-directional
channels and communication but the extension to bi-directional channel can be
considered as the union of two unidirectional channels. A mono-directional
channel is defined by the assertions sent or received (over the channel).

\begin{definition}{\bf mono-directional channel --}\label{def:monochannel}
	Given two agents $s$ (sender) and $r$ (receiver) a
	mono-directional channel $s \rightarrow r$ is defined as the union of all the assertions 
	$\rassert{s}{r}$ sent by $s$ to $r$ ($\assertionRegion_s$) and received by $r$ from $s$ ($\assertionRegion_r$). 
\end{definition}
The \emph{quality of a mono-directional} channel is defined as the 
$\rcc$ relation between the assertions made by the sender and the ones received by the receiver, i.e. $\Rcc{s}{r}$.

@@

\Paragraph{Port weaknesses}
From this definition, it follows that there exist only the following types of insecure port in RCC5:
\begin{itemize}
	\item \emph{drop port} ($s\dropport a$), where assertions reaches the port but do not pass the boundary of the agent (i.e. do not become belief of the agent)
	\item \emph{insertion port} ($s\insertport a$), where some new information is believed by $a$ as incoming from the port but $s$ didn't send it
	\item \emph{injection port} ($s\injectionport a$), where information coming from $s$ is substituted with new information which becomes believed by $a$
	\item \emph{selective port}, where some
		information passes the port while other is either dropped
		($s\selectivedropport a$), inserted
		($s\selectiveinsertport a$), or injected
		($s\selectiveinjectionport a$)
\end{itemize}

@@

@@

@@

Non-repudiation: the ability to ensure that a party to a contract or a
communication cannot deny the authenticity of their signature on information
(or the sending of) that they originated.  If information X arrives from A, A
sent it and cannot deny it (partial overlap??).  If sender A sends information
X, it cannot say he didn't do it.  Non-repudiation implies authenticity and
integrity. Authenticity doesn't imply non-repudiation (replay attacks?).
Integrity doesn't imply non-repudiation (replay attacks?).

\begin{enumerate}
\item specification -- definition of the desired design of a system. The
specification is verified w.r.t. the  $\abf$ theory. Checking the
controls of the whole cybersecurity life-cycle and the relation with
CWE.
\item design -- the mitigations identified in the specification stage
are implemented into the design. The security of the assets w.r.t. the design are
verified with a, so called, cybersecurity risk assessment.
\end{enumerate}
}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=.9\textwidth]{channel.pdf}
	\caption{Communication over a Mono-directional Channel}
	\label{fig:channel}
\end{figure}

While \emph{agents} and \emph{communication} between agents are described and
defined in Section~\ref{sec:theory}, the concepts of \emph{port} (depicted in
Figure~\ref{fig:ioports}), \emph{channel} (depicted in
Figure~\ref{fig:channel}), \emph{functional and physical architecture}, and
\emph{functional block} have not yet been defined with respect to the
$\abf$-theory.  Informally, a channel\footnote{for now, we rely on the
intuitive notion of channel as ``something'' that transfers information as
Assertions between output and input port, i.e. monodirectional} identifies the
place where the communication takes place.  In this work, we only consider
mono-directional channels and communication but the extension to bi-directional
channel can be considered as the union of two unidirectional channels. A
mono-directional channel is defined by the assertions sent or received (over
the channel).

\Paragraph{Input and Output Ports}
Since the $\abf$-theory is a theory of agents, we consider ports as agents that
allows the exchange of information between a channel and another
agent.  However, a port must be considered as a special type of agent to avoid
an \emph{infinite regress} in which a port needs a port to transfer information
between the outside of the port to the inside of itself.

@@

\Paragraph{Port Weaknesses}
From this definition, it follows that there exist only the following \emph{six} types of weaknesses, generating six types of insecure port in RCC5:
\begin{enumerate}[start=1, label={W\arabic*)}]
	\item \emph{drop port} ($s\dropport a$), where assertions reaches the port but do not pass the boundary of the agent (i.e. do not become belief of the agent)
	\item \emph{insertion port} ($s\insertport a$), where some new information is believed by $a$ as incoming from the port but $s$ didn't send it
	\item \emph{injection port} ($s\injectionport a$), where information coming from $s$ is substituted with new information which becomes believed by $a$
	\item \emph{selective port}, where some information passes the port and part is either:
	\begin{enumerate}[start=1, label={W4.\arabic*)}]
		\item dropped ($s\selectivedropport a$), 
		\item inserted ($s\selectiveinsertport a$), or
		\item injected ($s\selectiveinjectionport a$)
\end{enumerate}
\end{enumerate}

@@

	In other words, $\dr{\assertionRegion}{\beliefRegion}\equiv\neg\overlaps{\assertionRegion}{\beliefRegion}\equiv\neg(\varphi\subseteq\assertionRegion\wedge\varphi\subseteq\beliefRegion)\equiv\varphi\not\subseteq\assertionRegion\vee\varphi\not\subseteq\beliefRegion$

@@

\Paragraph{Communication Channels}
We start by considering the difference between a (communication)
mono-directional channel (channel from now on) and an agent, as we did for the
ports, since the $\abf$-theory is a theory of agents.  In fact, if a channel
were considered an agent (channel-agent) then the question would be how an
agent would transfer its Assertions to the channel-agent. If the channel
between the agent and the channel-agent is again an agent, we would generate an
\emph{infinite regress}. Therefore, we do allow channel-agents but we assume
a finite depth (of detail) for a channel, where there exists a bottom-channel 
which is not an agent. For now, we do not constrain a channel-agent in any way
so there is no difference between a channel agent and agent. Therefore, for
the sake of simplicity, we consider, in this text, channels to be bottom-channels,
defined as agents with the pre-defined behavior of storing Assertions that are transferred
over them (i.e. over the channel we are defining).

\begin{definition}{\bf Mono-directional Channel --}\label{def:monochannel}
	Given two agents $s$ (sender) and $r$ (receiver) a
	mono-directional channel $s \rightarrow r$ is defined as the union of all the assertions 
	$\rassert{s}{r}$ sent by $s$ to $r$ ($\assertionRegion_s$) and received by $r$ from $s$ ($\assertionRegion_r$) (for any given instance of time). 
\end{definition}
The \emph{quality of a mono-directional} channel is defined as the 
$\rcc$ relation between the Assertions made by the sender and the ones received by the receiver, i.e. $\Rcc{\assertionRegion_s}{\beliefRegion_r}$.

\Paragraph{Channel Weaknesses}

@@

Non-repudiation: the ability to ensure that a party to a contract or a
communication cannot deny the authenticity of their signature on information
(or the sending of) that they originated.  If information X arrives from A, A
sent it and cannot deny it (partial overlap??).  If sender A sends information
X, it cannot say he didn't do it.  Non-repudiation implies authenticity and
integrity. Authenticity doesn't imply non-repudiation (replay attacks?).
Integrity doesn't imply non-repudiation (replay attacks?). 
}
\subsection{Abstraction Level of a Specification in $\abf$-theory}
As highlighted in \autocite{}, ``The level of abstraction is always a concern
when it come sto the definition of a system model.'' (as we already mentioned in Section~\ref{sec:problem}).
